\documentclass[a4paper,11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumerate}
\usepackage{xcolor}
 \usepackage{qtree}
\usepackage{fge}
\usepackage{tgtermes}

\usepackage{tikz}
\usepackage{tikz-qtree}

\usepackage{amsmath,amsthm, amssymb, latexsym}
\usepackage{graphicx, fancyhdr}
 \usepackage{stmaryrd}
 \usepackage{mathrsfs}
\usepackage{soul}
 \usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{ot-tableau}
\usepackage{multicol}
\usepackage{enumitem}

\usepackage{tipa}
\usepackage{tipx}

\usepackage[sc]{mathpazo}
\usepackage[scaled=0.95]{helvet}
\usepackage{courier}
\usepackage{tgpagella}
\usepackage[euler]{textgreek}
 
\usepackage{gb4e}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{Ling201:02 \hfill 2025}
\fancyfoot[C]{\thepage}

\renewcommand{\theenumi}{\Alph{enumi}}


\begin{document}

\begin{center}
\Large{\textbf{Week 5 Recitation}}
\end{center}


\section{Phrase structure rules (PSR)}

\begin{itemize}
\item[] TP $\rightarrow$ NP (T) VP
\item[] NP $\rightarrow$ (D) (AdjP+) N (PP+)
\item[] NP $\rightarrow$ N 
\item[] PP $\rightarrow$ P NP
\item[] VP $\rightarrow$ (AdvP+) V (NP) (AdvP+) (PP+) (AdvP+)
\item[] AdjP $\rightarrow$ (AdvP) Adj
\item[] AdvP $\rightarrow$ (AdvP) Adv
\end{itemize}

\section{Practice}
\subsection{Phrases}

\begin{exe}
\ex an apple
\ex the bright sun
\ex into the building 
\ex peas in a pod
\ex wonderfully fresh bread
\ex really slowly
\ex the dog with the collar in the park
\ex the man in the car with the flat tire
\end{exe}

\subsection{Sentences}

\begin{exe}
\ex The robin caught a worm.
\ex The mockingbird was singing.
\ex The sparrow on the windowsill chirped loudly.
\ex The osprey brought its hungry chicks a fish.
\ex The large owl lives in a nest in the barn.
\ex The duck quickly led her ducklings across the street.
\end{exe}

\subsection{\textbf{Bonus:} complex sentences}

\begin{exe}
\ex John said that he likes pizza. 
\ex I want to go to California.
\ex I saw a deer that was grazing in the park. 
\end{exe}



\end{document}